### 2013-11-11 src2/thesis.tex
update

Since our work with ArBB, Intel has unfortunately retired the ArBB system. This 
leaves EmbArBB without a functioning code generating backend. This makes the choice of a
deep embedding (in hindsight) the correct one. EmbArBB could be resurrected by implementing 
a new code generating backend.

@@

>>>>

Since our work with ArBB, Intel has unfortunately retired the ArBB system. This 
leaves EmbArBB without a functioning code generating backend. This makes the choice of a
deep embedding (in hindsight) the correct one. EmbArBB could be resurrected by implementing 
a new code generating backend. However, a complete reimplementation of the ArBB API would be 
a massive undertaking.

@@

Obsidian constrains the programmer into writing programs that we can easily compile to 
CUDA. This is done by modelling the GPU programming in types attached to programs. A 
currently ongoing master's project is investigating what effects removing these 
types have. It is clear that if the programmer is not constrained to writing flat 
(or very limited nested) programs, transformations are needed on the AST before 
generating CUDA code.
